How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering
\includegraphics[width = 0.9 \textwidth]{./figs/fig6.pdf}
\caption{
Tortuosity statistics from an ensemble of simulations. (a)--(b) The longitudinal (a) and transverse tortuosity measurements are well grouped with respect to the number of bodies. (c)--(e) Statistics of the ratio, $(T_2 -1)/(T_1 -1)$, including its configurational and shape contribution.
\label{fig6}
}
\end{figure*}
%---------------------------------------------------------%

>>>>

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering
\includegraphics[width = 0.9 \textwidth]{./figs/fig6.pdf}
\caption{
Tortuosity statistics from an ensemble of simulations. (a) \nick{WRITE STUFF}
(c)--(e) Statistics of the ratio, $(T_2 -1)/(T_1 -1)$, including its configurational and shape contribution.
\label{fig6}
}
\end{figure*}
%---------------------------------------------------------%

%(a)--(b) The longitudinal (a) and transverse (b) tortuosity measurements are well grouped with respect to the number of bodies.
